Type Refinements for the Working Class

### 2015-11-26 paper.tex
Update notation
wording

\newcommand\Symbols{\mathbf{I}}
\newcommand\SymSets{\mathbb{F}_\Symbols}
\newcommand\FinSets{\mathbb{F}}
\newcommand\CanOperators{\mathcal{K}}

@@

Martin-L\"of's key innovation was the commitment to pervasive functionality
(extensionality) as part of the \emph{definitions} of the judgments and the
types, in contrast to the state of affairs in formal type theory where
functionality is a metatheorem which must be shown to obtain, based on the
(somewhat arbitrary) equational theory which has been imposed. Furthermore,
models for behavioral type theory interpret the types as partial equivalence
relations on only closed terms, and the meaning of the hypothetical judgment is
defined separately and uniformly in the logical relations style.

@@

\begin{definition}
  To know $\Refines{\Upsilon}{\phi}{\tau}$ (presupposing $\IsSymCtx{\Upsilon}$
  and $\IsSort{\tau}$) is to know, for any
  \begin{tikzcd}[cramped]
    \IMode{\Upsilon}\arrow[r,hook,"\IMode{\rho}"] &\IMode{\Upsilon'}
  \end{tikzcd},
  what it means for any $\Member{M,N}{\Exprs_\tau(\Upsilon')}$ to be equated by
  $\phi$ (written $\RefEquate{\phi}{\rho}{M}{N}$), such that
  $\RefEquate{\phi}{\rho}{-}{-}$ is a partial equivalence relation on
  $\Exprs_\tau(\Upsilon')$. Morever, that for any
  \begin{tikzcd}[cramped]
    \IMode{\Upsilon'}\arrow[r,hook,"\IMode{\rho'}"] &\IMode{\Upsilon''}
  \end{tikzcd},
  from $\RefEquate{\phi}{\rho}{M}{N}$ we may conclude
  $\RefEquate{\phi}{\rho'\circ\rho}{M\rho'}{N\rho'}$.
\end{definition}

@@

  At this point, it should be noted that this is very similar to the semantical
  explanation of typehood given in \cite{martin-lof:1979}, except that we have
  generalized it to a multi-sorted setting, and that we have fibred the entire
  apparatus over collections $\Upsilon$ of symbols.

@@

@@

  To know $\IsSubrefinement{\Upsilon}{\phi}{\psi}{\tau}$ (presupposing
  $\Refines{\Upsilon}{\phi}{\tau}$ and $\Refines{\Upsilon}{\psi}{\tau}$) , is
  to know, for any renamings
  \begin{tikzcd}[cramped]
    \IMode{\Upsilon} \arrow[r, hook, "\IMode{\rho}"]
    & \IMode{\Upsilon'} \arrow[r, hook, "\IMode{\rho'}"]
    & \IMode{\Upsilon''}
  \end{tikzcd},
  that from $\RefEquate{\phi}{\rho}{M}{N}$ you can conclude
  $\RefEquate{\psi}{\rho'\circ\rho}{M\rho'}{N\rho'}$ for any
  $\Member{M,N}{\Exprs_\tau(\Upsilon')}$.

@@

Two refinements are equal when they denote the same PER. That is, we have
$\EqRefines{\Upsilon}{\phi}{\psi}{\tau}$ just when both
$\IsSubrefinement{\Upsilon}{\phi}{\psi}{\tau}$ and
$\IsSubrefinement{\Upsilon}{\psi}{\phi}{\tau}$.

@@

The primary judgment concerning refinements is the parametric equality,
$\RMemEq{\Upsilon}{M}{N}{\phi}$, which presupposes
$\Refines{\Upsilon'}{\phi}{\tau}$ for some $\Upsilon'$ such that we have
\begin{tikzcd}[cramped, sep = small]
  \IMode{\Upsilon'} \arrow[r, hook, "\IMode{\rho}"] &\IMode{\Upsilon}
\end{tikzcd},
and $\Member{M,N}{\Exprs_\tau(\Upsilon)}$. The meaning of this judgment is
that $M$ and $N$ are identified by $\phi$ at $\Upsilon$:
\[
  \infer{
    \RMemEq{\Upsilon}{M}{N}{\phi}
  }{
    \RefEquate{\phi}{\rho}{M}{N}
  }
\]

@@

For a context refinement $\RefinesCtx{\Upsilon}{\Psi}{\Gamma}$ and a renaming
\begin{tikzcd}[cramped]
  \IMode{\Upsilon} \arrow[r,hook,"\IMode{\rho}"] &\IMode{\Upsilon'}
\end{tikzcd},
we can define a new context refinement
$\RefinesCtx{\Upsilon'}{\Psi\rho}{\Gamma}$ by applying $\rho$ pointwise at
each of the sort refinements in the context.

@@

\begin{quote}
  To know $\FEqRefines{\Upsilon}{\Psi,x:\chi}{\phi}{\psi}{\tau}$ is to know, for any renaming
  \begin{tikzcd}[cramped]
    \IMode{\Upsilon} \arrow[r,hook,"\IMode{\rho}"] &\IMode{\Upsilon'}
  \end{tikzcd}
  and closed terms $\Member{M_0,M_1}{\Exprs_\sigma(\Upsilon')}$, that from
  $\FRMemEq{\Upsilon'}{\Psi\rho}{M_0}{M_1}{\chi\rho}$, you can conclude
  $\FEqRefines{\Upsilon'}{\Psi\rho}{\Subst{M_0}{x}{\phi\rho}}{\Subst{M_1}{x}{\psi\rho}}{\tau}$.
  In other words:
  %
  \[
    \infer[\PFunRefSnoc]{
      \FEqRefines{\Upsilon}{\Psi,x:\chi}{\phi}{\psi}{\tau}
    }{
      \begin{array}{l}
        \forall
        \begin{tikzcd}[cramped, ampersand replacement = \&]
          \IMode{\Upsilon} \arrow[r,hook,"\IMode{\rho}"] \&\IMode{\Upsilon'}
        \end{tikzcd}.\
        \forall \Member{M_0,M_1}{\Exprs_\sigma(\Upsilon')}.\\
        \left(\FRMemEq{\Upsilon'}{\Psi\rho}{M_0}{M_1}{\chi\rho}\right)
        \Rightarrow
        \left(\FEqRefines{\Upsilon'}{\Psi\rho}{\Subst{M_0}{x}{\phi\rho}}{\Subst{M_1}{x}{\psi\rho}}{\tau}\right)
      \end{array}
    }
  \]
\end{quote}

@@

\paragraph{Case} $\DefRefinesCtxSnoc{\Upsilon}{\Psi}{x}{\chi}{\Gamma}{\sigma}$.
\begin{quote}
  To know $\FRMemEq{\Upsilon}{\Psi,x:\chi}{N_0}{N_1}{\phi}$ is to know, for any renaming
  \begin{tikzcd}[cramped]
    \IMode{\Upsilon} \arrow[r,hook,"\IMode{\rho}"] &\IMode{\Upsilon'}
  \end{tikzcd}
  and closed terms $\Member{M_0,M_1}{\Exprs_\sigma(\Upsilon')}$, that from
  $\FRMemEq{\Upsilon'}{\Psi\rho}{M_0}{M_1}{\chi\rho}$, you can conclude
  $\FRMemEq{\Upsilon'}{\Psi\rho}{\Subst{M_0}{x}{N_0\rho}}{\Subst{M_1}{x}{N_1\rho}}{\Subst{M_0}{x}{\phi\rho}}$.
  In other words:
  %
  \[
    \infer{
      \FRMemEq{\Upsilon}{\Psi,x:\psi}{N_0}{N_1}{\phi}
    }{
      \begin{array}{l}
        \forall
        \begin{tikzcd}[cramped, ampersand replacement = \&]
          \IMode{\Upsilon} \arrow[r,hook,"\IMode{\rho}"] \&\IMode{\Upsilon'}
        \end{tikzcd}.\
        \forall \Member{M_0,M_1}{\Exprs_\sigma(\Upsilon')}.\\
        \left(\FRMemEq{\Upsilon'}{\Psi\rho}{M_0}{M_1}{\chi\rho}\right)
        \Rightarrow
        \left(%
          \FRMemEq{\Upsilon'}{\Psi\rho}{%
            \Subst{M_0}{x}{N_0\rho}
          }{%
            \Subst{M_1}{x}{N_1\rho}%
          }{\Subst{M_0}{x}{\phi\rho}
          }%
        \right)
      \end{array}
    }
  \]
\end{quote}
%%
%% \section{Constructions on Refinements}
%%
%% Refinements can be arranged in a partial order via the
%% $\IsSubrefinement{\Phi}{\phi}{\psi}{\tau}$ judgment, and admit a lattice structure
%% at any sort $\tau$.
%%
%% We have the bottom refinement $\GloballyRefines{\TyBot{\tau}}{\tau}$, which simply
%% contains no elements. Next, the top refinement $\GloballyRefines{\TyTop{\tau}}{\tau}$
%% identifies all terms $M,N$ such that $\IsAbt{\cdot}{\Upsilon}{\cdot}{M}{\tau}$
%% and $\IsAbt{\cdot}{\Upsilon}{\cdot}{N}{\tau}$. The join
%% $\Refines{\Phi}{\phi\TyJoin{\tau}\psi}{\tau}$ of two refinements
%% $\Refines{\Phi}{\phi}{\tau}$ and $\Refines{\Phi}{\psi}{\tau}$ is defined as follows:
%% \begin{gather*}
%%   \infer{
%%     \RMemEq{\Phi}{M}{N}{\phi\TyJoin{\tau}\psi}
%%   }{
%%     \RMemEq{\Phi}{M}{N}{\phi}
%%   }\qquad
%%   \infer{
%%     \RMemEq{\Phi}{M}{N}{\phi\TyJoin{\tau}\psi}
%%   }{
%%     \RMemEq{\Phi}{M}{N}{\psi}
%%   }
%% \end{gather*}
%%
%% Finally the meet $\Refines{\Phi}{\phi\TyMeet{\tau}\psi}{\tau}$ of two refinements
%% $\Refines{\Phi}{\phi}{\tau}$ and $\Refines{\Phi}{\psi}{\tau}$ is defined
%% dually:
%% \[
%%   \infer{
%%     \RMemEq{\Phi}{M}{N}{\phi\TyMeet{\tau}\psi}
%%   }{
%%     \RMemEq{\Phi}{M}{N}{\phi} &
%%     \RMemEq{\Phi}{M}{N}{\psi}
%%   }
%% \]
%%
%% It is trivial to verify that these constructions on refinements give rise to a
%% lattice.
%%
%% \section{Multi-Sorted Computational Type Theory}
%%
%% Martin-L\"of's type theory is a theory of \emph{value types}: to define a type,
%% you specify how to form its equal canonical inhabitants, or values. Then, the
%% inhabitants of the types are explained uniformly by extending this relation
%% over an operational semantics such that two terms are equal members of a
%% type just when they compute to equal values of that type.
%%
%% More generally, one may wish to consider types which include computations in
%% addition to values; an example of such a type would be $\bar{\psi}$ when $\psi$
%% is a type, which would include all the members of $\psi$ as well as a divergent
%% computation. Another example is the type $\TyTop{\tau}$ which identifies all
%% closed terms of sort $\tau$.
%%
%% In order to ensure that such types are sensible, we must formulate a notion of
%% computational equivalence, and then say that a refinement is a \emph{type} just
%% when it respects computational equivalence; then, we are able to define types
%% as PERs on \emph{programs} in addition to values.

@@

\begin{remark}
  In any topos $\mathcal{E}$, for an object $X$ we can define the object of
  relations on $X$ as the exponential $\Define{\Pow{X}}{\Omega^X}$. Then, the
  data of such a relation is contained in a natural transformation
  $\Of{R}{\Hom{\mathcal{E}}{\mathbb{1}}{\Pow{X}}}$.
\end{remark}

@@

Now, we can extend $R_\tau$ to a new relation $[R_\tau]$ on closed expressions
which respects a single ``layer'' of computation. We will say
$\SBinRel{[R_\tau]}{\Upsilon}{M}{N}$ when, supposing
$\Eval{\Upsilon}{\tau}{M}{\App{\vartheta}{\Vec{E}}}$ such that
$\IMode{\Upsilon}\Vdash_{\IMode{\CanOperators}}\IMode{\vartheta}:\OMode{\MkArity{\vec{v}}{\tau}}$,
for any
\begin{tikzcd}[cramped]
  \IMode{\Upsilon} \arrow[r,hook,"\IMode{\rho}"] &\IMode{\Upsilon'}
\end{tikzcd},
we have $\Eval{\Upsilon'}{\tau}{N\rho}{\App{\vartheta\rho}{\Vec{F}\rho}}$ and
$\SBinRel{R_{\vec{v}}}{\Upsilon'}{\vec{E}\rho}{\vec{F}\rho}$.

>>>>

\newcommand\CanOperators{\mathcal{K}}

@@

Martin-L\"of's key innovation was the commitment to pervasive functionality
(extensionality) as part of the \emph{definitions} of the judgments and the
types, in contrast to the state of affairs in formal type theory where
functionality is a metatheorem which must be shown to obtain, based on the
(somewhat arbitrary) equational theory which has been imposed. Furthermore,
models for behavioral type theory interpret the types as partial equivalence
relations (PER) on only closed terms, and the meaning of the hypothetical
judgment is defined separately and uniformly in the logical relations style.

@@

\begin{definition}
  To know $\Refines{\Upsilon}{\phi}{\tau}$ (presupposing $\IsSymCtx{\Upsilon}$
  and $\IsSort{\tau}$) is to know, for any
  \begin{tikzcd}[cramped]
    \IMode{\Upsilon}\arrow[r,hook,"\IMode{\rho}"] &\IMode{\Upsilon'}
  \end{tikzcd}
, what it means for any $\Member{M,N}{\Exprs_\tau(\Upsilon')}$ to be equated by
  $\phi$ (written $\RefEquate{\phi}{\rho}{M}{N}$), such that
  $\RefEquate{\phi}{\rho}{-}{-}$ is a partial equivalence relation (PER) on
  $\Exprs_\tau(\Upsilon')$. Morever, that for any
  \begin{tikzcd}[cramped]
    \IMode{\Upsilon'}\arrow[r,hook,"\IMode{\rho'}"] &\IMode{\Upsilon''}
  \end{tikzcd}
,
  from $\RefEquate{\phi}{\rho}{M}{N}$ we may conclude
  $\RefEquate{\phi}{\rho'\circ\rho}{M\rho'}{N\rho'}$.
\end{definition}

@@

  At this point, it should be noted that this is very similar to the semantical
  explanation of typehood given in~\cite{martin-lof:1979}, except that we have
  generalized it to a multi-sorted setting, and that we have fibred the entire
  apparatus over collections $\Upsilon$ of symbols.

@@

  It should be noted that PERs can be understood as 0-semigroupoids. In other
  words, these are 1-groupoids without identity morphisms and without coherence
  laws regarding composition and inverse operations. This distinction is
  especially relevant in formal type theory where groupoids ``one dimension
  down'' are not sets but setoids (i.e., groupoids sans coherence). Thus, a PER
  can formally be thought of as a kind of partial setoid that facilitates
  constructions on subsets in addition to quotients. \todo[inline]{Say something
    about internal (semi)-groupoids?}

@@

  To know $\IsSubrefinement{\Upsilon}{\phi}{\psi}{\tau}$ (presupposing
  $\Refines{\Upsilon}{\phi}{\tau}$ and $\Refines{\Upsilon}{\psi}{\tau}$), is
  to know, for any renamings
  \begin{tikzcd}[cramped]
    \IMode{\Upsilon} \arrow[r, hook, "\IMode{\rho}"]
    & \IMode{\Upsilon'} \arrow[r, hook, "\IMode{\rho'}"]
    & \IMode{\Upsilon''}
  \end{tikzcd}
, that from $\RefEquate{\phi}{\rho}{M}{N}$ you can conclude
  $\RefEquate{\psi}{\rho'\circ\rho}{M\rho'}{N\rho'}$ for any
  $\Member{M,N}{\Exprs_\tau(\Upsilon')}$.

@@

Two refinements are equal when they denote the same PER.\@That is, we have
$\EqRefines{\Upsilon}{\phi}{\psi}{\tau}$ just when both
$\IsSubrefinement{\Upsilon}{\phi}{\psi}{\tau}$ and
$\IsSubrefinement{\Upsilon}{\psi}{\phi}{\tau}$.

@@

The primary judgment concerning refinements is the parametric equality,
$\RMemEq{\Upsilon}{M}{N}{\phi}$, which presupposes
$\Refines{\Upsilon'}{\phi}{\tau}$ for some $\Upsilon'$ such that we have
\begin{tikzcd}[cramped, sep = small]
  \IMode{\Upsilon'} \arrow[r, hook, "\IMode{\rho}"] &\IMode{\Upsilon}
\end{tikzcd}
, and $\Member{M,N}{\Exprs_\tau(\Upsilon)}$. The meaning of this judgment is
that $M$ and $N$ are identified by $\phi$ at $\Upsilon$:
\[
  \infer{
    \RMemEq{\Upsilon}{M}{N}{\phi}
  }{
    \RefEquate{\phi}{\rho}{M}{N}
  }
\]

@@

For a context refinement $\RefinesCtx{\Upsilon}{\Psi}{\Gamma}$ and a renaming
\begin{tikzcd}[cramped]
  \IMode{\Upsilon} \arrow[r,hook,"\IMode{\rho}"] &\IMode{\Upsilon'}
\end{tikzcd}
, we can define a new context refinement
$\RefinesCtx{\Upsilon'}{\Psi\rho}{\Gamma}$ by applying $\rho$ pointwise at
each of the sort refinements in the context.

@@

\begin{quote}
  To know $\FEqRefines{\Upsilon}{\Psi,x:\chi}{\phi}{\psi}{\tau}$ is to know, for any renaming
  \begin{tikzcd}[cramped]
    \IMode{\Upsilon} \arrow[r,hook,"\IMode{\rho}"] &\IMode{\Upsilon'}
  \end{tikzcd}
  and closed terms $\Member{M_0,M_1}{\Exprs_\sigma(\Upsilon')}$, that from
  $\FRMemEq{\Upsilon'}{\Psi\rho}{M_0}{M_1}{\chi\rho}$, you can conclude
  $\FEqRefines{\Upsilon'}{\Psi\rho}{\Subst{M_0}{x}{\phi\rho}}{\Subst{M_1}{x}{\psi\rho}}{\tau}$.
  In other words:
  %
  \[
    \infer[\PFunRefSnoc]{
      \FEqRefines{\Upsilon}{\Psi,x:\chi}{\phi}{\psi}{\tau}
    }{
      \begin{array}{l}
        \forall
        \begin{tikzcd}[cramped, ampersand replacement = \&]
          \IMode{\Upsilon} \arrow[r,hook,"\IMode{\rho}"] \&\IMode{\Upsilon'}
        \end{tikzcd}
        .\ \forall \Member{M_0,M_1}{\Exprs_\sigma(\Upsilon')}.\\
        \left(\FRMemEq{\Upsilon'}{\Psi\rho}{M_0}{M_1}{\chi\rho}\right)
        \Rightarrow
        \left(\FEqRefines{\Upsilon'}{\Psi\rho}{\Subst{M_0}{x}{\phi\rho}}{\Subst{M_1}{x}{\psi\rho}}{\tau}\right)
      \end{array}
    }
  \]
\end{quote}

@@

\paragraph{Case} $\DefRefinesCtxSnoc{\Upsilon}{\Psi}{x}{\chi}{\Gamma}{\sigma}$.
\begin{quote}
  To know $\FRMemEq{\Upsilon}{\Psi,x:\chi}{N_0}{N_1}{\phi}$ is to know, for any renaming
  \begin{tikzcd}[cramped]
    \IMode{\Upsilon} \arrow[r,hook,"\IMode{\rho}"] &\IMode{\Upsilon'}
  \end{tikzcd}
  and closed terms $\Member{M_0,M_1}{\Exprs_\sigma(\Upsilon')}$, that from
  $\FRMemEq{\Upsilon'}{\Psi\rho}{M_0}{M_1}{\chi\rho}$, you can conclude
  $\FRMemEq{\Upsilon'}{\Psi\rho}{\Subst{M_0}{x}{N_0\rho}}{\Subst{M_1}{x}{N_1\rho}}{\Subst{M_0}{x}{\phi\rho}}$.
  In other words:
  %
  \[
    \infer{
      \FRMemEq{\Upsilon}{\Psi,x:\psi}{N_0}{N_1}{\phi}
    }{
      \begin{array}{l}
        \forall
        \begin{tikzcd}[cramped, ampersand replacement = \&]
          \IMode{\Upsilon} \arrow[r,hook,"\IMode{\rho}"] \&\IMode{\Upsilon'}
        \end{tikzcd}
        .\ \forall \Member{M_0,M_1}{\Exprs_\sigma(\Upsilon')}.\\
        \left(\FRMemEq{\Upsilon'}{\Psi\rho}{M_0}{M_1}{\chi\rho}\right)
        \Rightarrow
        \left(%
          \FRMemEq{\Upsilon'}{\Psi\rho}{%
            \Subst{M_0}{x}{N_0\rho}
          }{%
            \Subst{M_1}{x}{N_1\rho}%
          }{\Subst{M_0}{x}{\phi\rho}
          }%
        \right)
      \end{array}
    }
  \]
\end{quote}
%%
%% \section{Constructions on Refinements}
%%
%% Refinements can be arranged in a partial order via the
%% $\IsSubrefinement{\Phi}{\phi}{\psi}{\tau}$ judgment, and admit a lattice structure
%% at any sort $\tau$.
%%
%% We have the bottom refinement $\GloballyRefines{\TyBot{\tau}}{\tau}$, which simply
%% contains no elements. Next, the top refinement $\GloballyRefines{\TyTop{\tau}}{\tau}$
%% identifies all terms $M,N$ such that $\IsAbt{\cdot}{\Upsilon}{\cdot}{M}{\tau}$
%% and $\IsAbt{\cdot}{\Upsilon}{\cdot}{N}{\tau}$. The join
%% $\Refines{\Phi}{\phi\TyJoin{\tau}\psi}{\tau}$ of two refinements
%% $\Refines{\Phi}{\phi}{\tau}$ and $\Refines{\Phi}{\psi}{\tau}$ is defined as follows:
%% \begin{gather*}
%%   \infer{
%%     \RMemEq{\Phi}{M}{N}{\phi\TyJoin{\tau}\psi}
%%   }{
%%     \RMemEq{\Phi}{M}{N}{\phi}
%%   }\qquad
%%   \infer{
%%     \RMemEq{\Phi}{M}{N}{\phi\TyJoin{\tau}\psi}
%%   }{
%%     \RMemEq{\Phi}{M}{N}{\psi}
%%   }
%% \end{gather*}
%%
%% Finally the meet $\Refines{\Phi}{\phi\TyMeet{\tau}\psi}{\tau}$ of two refinements
%% $\Refines{\Phi}{\phi}{\tau}$ and $\Refines{\Phi}{\psi}{\tau}$ is defined
%% dually:
%% \[
%%   \infer{
%%     \RMemEq{\Phi}{M}{N}{\phi\TyMeet{\tau}\psi}
%%   }{
%%     \RMemEq{\Phi}{M}{N}{\phi} &
%%     \RMemEq{\Phi}{M}{N}{\psi}
%%   }
%% \]
%%
%% It is trivial to verify that these constructions on refinements give rise to a
%% lattice.
%%
%% \section{Multi-Sorted Computational Type Theory}
%%
%% Martin-L\"of's type theory is a theory of \emph{value types}: to define a type,
%% you specify how to form its equal canonical inhabitants, or values. Then, the
%% inhabitants of the types are explained uniformly by extending this relation
%% over an operational semantics such that two terms are equal members of a
%% type just when they compute to equal values of that type.
%%
%% More generally, one may wish to consider types which include computations in
%% addition to values; an example of such a type would be $\bar{\psi}$ when $\psi$
%% is a type, which would include all the members of $\psi$ as well as a divergent
%% computation. Another example is the type $\TyTop{\tau}$ which identifies all
%% closed terms of sort $\tau$.
%%
%% In order to ensure that such types are sensible, we must formulate a notion of
%% computational equivalence, and then say that a refinement is a \emph{type} just
%% when it respects computational equivalence; then, we are able to define types
%% as PERs on \emph{programs} in addition to values.

@@

\begin{remark}
  In any topos $\mathcal{E}$, for an object $X$ we can define the object of
  relations on $X$ as the exponential $\Define{\Pow{X}}{\Omega^X}$. Then, the
  data of such a relation is contained in a global section
  $\Of{R}{\Hom{\mathcal{E}}{\mathbb{1}}{\Pow{X}}}$.
\end{remark}

@@

Now, we can extend $R_\tau$ to a new relation $[R_\tau]$ on closed expressions
which respects a single ``layer'' of computation. We will say
$\SBinRel{[R_\tau]}{\Upsilon}{M}{N}$ when, supposing
$\Eval{\Upsilon}{\tau}{M}{\App{\vartheta}{\Vec{E}}}$ such that
$\IMode{\Upsilon}\Vdash_{\IMode{\CanOperators}}\IMode{\vartheta}:\OMode{\MkArity{\vec{v}}{\tau}}$,
for any
\begin{tikzcd}[cramped]
  \IMode{\Upsilon} \arrow[r,hook,"\IMode{\rho}"] &\IMode{\Upsilon'}
\end{tikzcd}
, we have $\Eval{\Upsilon'}{\tau}{N\rho}{\App{\vartheta\rho}{\Vec{F}\rho}}$ and
$\SBinRel{R_{\vec{v}}}{\Upsilon'}{\vec{E}\rho}{\vec{F}\rho}$.
